\documentclass[a4paper,12pt]{article}

\usepackage[margin=0.2in, top=0.2in]{geometry}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=black]{hyperref}
\usepackage{enumitem}

\begin{document}


% Header 
\begin{center}
{\Huge \textbf{Abdelrahman Alnabawy}}\\[-0.0em]
{\Large Software Developer}\\[0.2em]
{5th District, 6th of October}\\
{\href{tel:+201554867970}{Phone}}
{\href{mailto:abderahman.elnabawy@gmail.com}{Email}}
{\href{https://www.linkedin.com/in/abdelrahman-elnabawy-363b63353/}{linkedin}}
{\href{https://github.com/abdelrahmanelnabawy}{Github}}
{\href{https://x.com/Abdelraalnabawy}{X}}
{\href{https://www.facebook.com/profile.php?id=61569052322072}{Facebook}}
{\href{https://www.instagram.com/abderahman.elnabawy/}{Instagram}}
{\href{https://www.reddit.com/user/Ok-Database3374/}{Reddit}}

\end{center}

% Career Objective
\vspace{-1.3em}
\noindent\textbf{Career Objective:} Software Developer with 2+ years of experience building ERP and full-stack systems using Python, Odoo, and modern web technologies. Focused on scalable, maintainable, and efficient software design.
% Work Ex
\vspace{-1.9em}
\section*{Work Experience}
\vspace{-1em}

\noindent\textbf{Ministry of Interior of Egypt, Software Developer, September 2024 - November 2025}\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed an accounting system using \textbf{Odoo 18} to streamline financial operations.
    \item Designed and implemented a comprehensive \textbf{inventory management system} for store operations.
    \item Built a \textbf{personnel management system} to track soldiers’ records and service details.
    \item Developed a \textbf{mobile application} for quick and secure access to soldiers’ information.
    \item Created a \textbf{gate control system} to record and monitor all entries and exits.
    \item Digitized and automated government workflows by converting manual records into digital systems.
    \item Optimized \textbf{Linux server performance} to support large-scale deployment and multi-service operations.
    \item Maintained and repaired computer systems to ensure consistent performance.
    \item Collaborated with the \textbf{Major General, Director of the Cairo Traffic Department}, and the \textbf{Brigadier General, Director of the Training and Recruits Department}, to align digital transformation goals with operational needs.
\end{itemize}

\noindent\textbf{IT-ARM, Odoo Developer, June 2024 - November 2024}\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed a complete POS system for a restaurant using Odoo 17.
    \item Built a dynamic and responsive user interface with the OWL framework.
\end{itemize}

\noindent\textbf{Ahram Canadian University, Odoo Developer, July 2023 – June 2024}\\[-1.2em]
\begin{itemize}[nosep]
    \item Implemented and customized ERP systems, including Accounting, HR, and Academic modules.
    \item Developed a Flutter mobile application for students to view personal data and request services.
    \item Configured a Linux server and deployed both the Odoo system and mobile app using Nginx for network management.
    \item Collaborated with clients to analyze requirements and deliver optimized, user-centered solutions.
    \item Used Jira for project management, sprint planning, and issue tracking.
\end{itemize}

\noindent\textbf{Upwork, Web Developer, June 2021 - September 2021 }\\[-1.2em]
\begin{itemize}[nosep]
    \item Assisted clients in designing and developing custom web applications.
    \item Maintained and debugged existing applications to ensure optimal performance and reliability.
    \item Applied \textbf{object-oriented programming (OOP)} principles and \textbf{software design patterns} to build scalable solutions.
    \item Communicated effectively with clients to gather requirements and deliver high-quality results.
\end{itemize}

\noindent\textbf{The Spark Foundation Internship – TSF, Web Developer, Augest 2021 - Augest 2021 }\\[-1.2em]
\begin{itemize}[nosep]
  \item Gained hands-on experience in building dynamic web applications.
    \item Developed object-oriented applications using \textbf{PHP}.
    \item Integrated and retrieved data efficiently from databases using \textbf{SQL}.
    \item Designed interactive user interfaces using \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript}, and modern front-end frameworks.
\end{itemize}



\vspace{-1.9em}
\section*{Education}
\vspace{-1em}

\noindent\textbf{Ahram Canadian University – ACU,BS in Computer Science, 2020 - 2024 }\\[-1.2em]
\begin{itemize}[nosep]
    \item Graduated with a \textbf{GPA of 3.48}, ranking \textbf{14th} in the class.
    \item Awarded for the \textbf{Best Graduation Project} among all projects of the academic year.
    \item Gained strong understanding of \textbf{algorithms}, \textbf{data structures}, and applying theoretical concepts to real-world applications.
    \item Improved \textbf{communication} and \textbf{teamwork} skills through collaborative projects and academic participation.
\end{itemize}

\noindent\textbf{American University in Cairo – AUC,English Courses, 2023 - 2024 }\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed effective communication skills in \textbf{English}, both written and verbal.
    \item Gained the ability to express ideas clearly and confidently in professional and academic contexts.
\end{itemize}

\noindent\textbf{Coursera – Online Learning Platform}\\[-1.2em]
\begin{itemize}[nosep]
    \item Completed multiple courses in core software engineering topics.
    \item Gained hands-on experience in \textbf{Object-Oriented Programming (OOP)} and \textbf{Design Patterns}.
    \item Strengthened understanding of \textbf{Algorithms} and their real-world applications.
    \item Learned modern \textbf{Web Development} practices, including front-end and back-end integration.
\end{itemize}

\vspace{-1.9em}
\section*{Skills}
\vspace{-1.0em}

\begin{itemize}[nosep]
    \item \textbf{Programming Languages:} Java, C/C++, Python, PHP, JavaScript, SQL
    \item \textbf{Web Technologies:} HTML, CSS, SASS, LESS, Web Development, API Integration
    \item \textbf{Frameworks \& Libraries:} Odoo, React, Spring Boot, Flutter, Flask, Bootstrap, jQuery, Handlebars, Twilight
    \item \textbf{Databases:} PostgreSQL, MySQL
    \item \textbf{DevOps \& Tools:} Linux, Shell Scripting, Docker, Nginx ,DevOps Practices
    \item \textbf{Machine Learning \& Data Science:} TensorFlow, PyTorch, Scikit-learn, OpenCV, Transformers, Pandas, NumPy, Matplotlib
    \item \textbf{Concepts:} Object-Oriented Programming (OOP), Software Design Patterns
\end{itemize}

\vspace{-1.9em}
\section*{Key Projects}
\vspace{-1.0em}
\noindent\textbf{Graduation Project – Medical Chatbot}\\[-1.2em]
\begin{itemize}[nosep]
    \item Selected among the \textbf{best graduation projects} at Ahram Canadian University.
    \item Designed and implemented the \textbf{medical text processing module} to analyze and generate intelligent medical responses.
    \item Achieved results with response accuracy remarkably close to that of professional doctors.
    \item Led one-third of the project, focusing on \textbf{NLP and medical dialogue systems}.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Transpolar (JS → Python Converter)}\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed a \textbf{Python-based converter} for translating JavaScript (.js) code into Python (.py).
    \item Implemented translation logic for syntax elements such as \textbf{if statements, loops, functions, and classes}.
    \item Strengthened understanding of \textbf{language design}, \textbf{syntax parsing}, and \textbf{cross-language logic mapping}.
\end{itemize}

\noindent\textbf{Movie and TV-Show System}\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed a media streaming platform using \textbf{React}, integrating multiple free APIs including \textbf{Vidsrc} for dynamic content sourcing.
    \item Identified inefficiencies in direct API requests and built a \textbf{centralized JavaScript API} to aggregate and streamline data delivery.
    \item Enhanced system performance and maintainability by optimizing API management and reducing redundant network calls.
\end{itemize}
\noindent\textbf{YouTube – Video Management System}\\[-1.2em]
\begin{itemize}[nosep]
    \item Built a full-stack video management platform using the \textbf{MAMP stack (MySQL, Apache, PHP)} along with \textbf{HTML}, \textbf{CSS}, and \textbf{JavaScript}.
    \item Implemented features for \textbf{video uploading, playback, and user interaction}, inspired by platforms like YouTube.
    \item Gained hands-on experience in \textbf{backend integration}, \textbf{database design}, and \textbf{frontend media rendering}.
\end{itemize}

\noindent\textbf{Simulator – NASA-Inspired Visualization}\\[-1.2em]
\begin{itemize}[nosep]
    \item Developed an \textbf{OpenGL}-based simulation inspired by NASA concepts to visualize size comparisons between Earth and other solar system objects.
    \item Designed and rendered \textbf{3D models} to illustrate planetary scale differences and spatial relationships.
    \item Strengthened skills in \textbf{computer graphics}, \textbf{3D rendering}, and \textbf{scientific visualization}.
\end{itemize}

\vspace{-1.9em}
\section*{Languages}
\vspace{-0.7em}
Arabic, English (\textbf{Advanced}); French, German (\textbf{Conversational})

\end{document}